---
title: "R_Review for Midterm"
author: "Yen Yee"
date: "07/05/2020"
output: html_document
---

# 1.Introduction to R  
### Basic Calculations 
  
* Power"^"  
* Remainder"%%"
  
#### Examples:  
```{r}
3^4 #power
31%%7 #remainder
```
### Usage of Function  
* **mean()** #Compute Average  
* **var()** #Compute Variance  

#### Example:  
```{r}
c<-1:11
mean(c)
var(c)
```
### Vectors  
* **c()**   
* **joint()**  
* Vector Calculation  

#### Example:  
```{r}
c(0,7,8) #c()is used to collect things into a vector 
x<-c(0,7,8)
numbers<-5:20
joint<-c(numbers,x) #join both vectors together
joint[5] #asking for the 5th index in the vector
joint[c(1,3,5,7)] #asking for multiple numbers
x[-2] #select all but the second element of x
x*3 #every element in vector x to be multiplied by 3
x-5 #every element in the vector x to minus 5
x^3 #every element in vector x to be in the power of 3
```
### Functions for Vectors  
* **seq()**   
* **rep()** 

#### Example:  
```{r}
seq(1,21,by=2)
rep(3,12) #number 3 to be repeated 12 times 
rep(c(1,4),c(3,2)) #number 1 to be repeated 3 times;number 4 to be repeated 2 times 
rep(c(1,4),each=3)
rep(seq(2,20,2),rep(2,10)) #every element to be repeated two times
```
* **substr(x,n,m)**  
* **paste()**  

#### Example:  
```{r}
colors<-c("red","yellow","blue")
more.colors<-c(colors,"green","magenta","cyan")
substr(colors,1,2)
paste(colors,"flowers")
paste("several",colors,"s",sep=" ")
paste("I like",colors,collapse=",")
```
**factor()**  
```{r}
grp<-c("cat","dog","cat","dog")
grp<-factor(grp)
grp
as.integer(grp)
levels(grp)
levels(grp)[as.integer(grp)]
```
**Matrix and Arrays**  
* **matrix()**  

#### Example:  
```{r}
m<-matrix(1:6,nrow=2,ncol=3)
m
m[1,2] #first column,second row
m[1,] #first column
m[,1] #first row
a<-array(1:24,c(3,4,2))
a
```
* **dataframe()**  

#### Example:  
```{r}
colors<-c("red","yellow","blue")
numbers<-c(1,2,3)
colors.and.numbers<-data.frame(colors,numbers,more.numbers=c(4,5,6))
colors.and.numbers
```

# 2.Built-in functions and online help  
q() is an example of a built-in function.There an many functions in R which are designed to do all sorts of things.The online help facility can help you to see what a particular function is supposed to do.  

**How to know the name of the function?**  
```{r}
#?mean 
#help(mean)
```
* **built-in graphic functions**  
```{r}
x<-c(12,15,13,20,14,16,10,8,15)
hist(x)
```
### Programming Statistical Graphics 

* **Bar Chart**  
```{r}
VADeaths
barplot(VADeaths,beside=TRUE,legend=TRUE,ylim=c(0,90),ylab="Deaths per 1000",main="Death rates in Virginia")
```

* **Dot Chart**  
```{r}
dotchart(VADeaths,xlim=c(0,75),lab="Deaths per 1000",main="Death rates in Virginia")
```

* **Histograms**  
```{r}
x<-rnorm(100)
hist(x)
```

* **Boxplot**
```{r}
boxplot(Sepal.Length~Species,data=iris,ylab="Sepal Length(cm)",main="Iris Measurements",boswex=0.5)
```

* **Scatterplots**  
```{r}
x<-rnorm(100)
y<-rpois(100,30)
plot(x,y,main="Poisson versus Normal")
```

* **QQPlots**  
```{r}
x<-rnorm(1000)
y<-rnorm(1000)
qqplot(x,y,main="x and y are the same")
B<-rnorm(1000,mean=3,sd=2)
qqplot(x,B,main="B is rescaled by x")
C<-rt(1000,df=2)
qqplot(x,C,main="C has heavier tails")
D<-exp(rnorm(1000))
qqplot(x,D,main="D is skewed to the right")
```

* **Adding additional information to the plots**  
```{r}
#Create a new dataframe 
sex <- c("M","F","M","F","F","M","F","M") 
length <- c(7.9,6.5,8.4,5.5,6.5,8.0,7.0,7.5) 
width <- c(2.3,1.7,2.6,1.7,1.9,2.1,1.8,1.9) 
indexfinger <- data.frame(sex,length,width) 
plot(width~length,data=indexfinger) 
#lighlight the longest male and female 
with(indexfinger[c(3,7),],points(length,width,pch=15)) #add linear regression for males 
abline(lm(width~length,data=indexfinger,subset=sex=="M"),lty=1) 
#add linear regression for females 
abline(lm(width~length,data=indexfinger,subset=sex=="F"),lty=2) 
#add legend for two lines 
legend("topleft",legend=c("Male","Female"),lty=1:2)
```

* **Annotate graphs outside the plot region**  
```{r}
par(mar=c(5,5,5,5)     +0.1) 
plot(c(1,9),c(0,50),type="n",xlab="",ylab="") 
text(6,40,"Plot region") 
points(6,20) 
text(6,20,"(6,20)",adj=c(0.5,2)) 
mtext(paste("Margin",1:4),side=1:4,line=3) 
mtext(paste("Line",0:4),side=1,line=0:4,,at=3,cex=0.6) 
mtext(paste("Line",0:4),side=2,line=0:4,,at=15,cex=0.6) 
mtext(paste("Line",0:4),side=3,line=0:4,,at=3,cex=0.6) 
mtext(paste("Line",0:4),side=4,line=0:4,,at=15,cex=0.6)
```

### Programming with R  

* **for loop**  
```{r}
Fibonacci <- numeric(12) 
Fibonacci[1] <- Fibonacci[2] <-1 
for (i in 3:12) Fibonacci[i] <- Fibonacci[i-2]+Fibonacci[i-1]
```

* **if()**
```{r}
corplot<-function(x,y,plotit){
  if (plotit == TRUE)
    plot(x,y)       
  cor(x,y)
}
corplot(c(2,5,7),c(5,6,8),FALSE)
```

* **Repeat** loop and the **break** and **next** statements  
```{r}
x<-3 
tolerance<-0.000001
repeat{
  f<-x^3+2*x^2-7   
  if (abs(f)<tolerance) break   
  f.prime<-3*x^2+4*x   
  x<-x-f/f.prime
}
x
```

### Simulation  
```{r}
random.number <- numeric(50) 
random.seed <- 27218 
for (j in 1:50){
  random.seed <- (171*random.seed) %% 30269
  random.number[j] <- random.seed/30269 
} 
random.number
```

* **Uniform Random Variable**  
```{r}
set.seed(32789) #ensures that output will match others 
runif(10,min=-3,max=-1)
```

* **Bernouli Random Variable**  
```{r}
set.seed(23207) 
guesses <- runif(20) 
correct.answers <- (guesses <0.2) 
correct.answers
table(correct.answers)
```

* **Binomial Random Variable**  
```{r}
#probability of getting four heads in six tosses of a fair coin 
dbinom(x=4,size=6,prob=0.5)
#cumulative probability(P(X<=4)) 
pbinom(4,6,0.5)
#the quantiles for the binomial distribution(89th percentile) 
qbinom(0.89,6,0.5)
```

* **Poisson** 
```{r}
dpois(x=3,0.5)
rpois(10,3.7)
```

### Computational Linear Algebra  
```{r}
H3 <- matrix(c(1,1/2,1/3,1/2,1/3,1/4,1/3,1/4,1/5),nrow=3) 
H3
1/cbind(seq(2,4),seq(2,4),seq(3,5))
1/rbind(seq(2,4),seq(2,4),seq(3,5))
matrix(seq(1,12),nrow=3)
x1 <- seq(1,3) 
x2 <- x1^2 
X <- cbind(x1,x2) 
X
X[3,2]
X[3,]
X[,2]
#if we want to maintain the result as a row or column vector ,use drop=FALSE 
X[3,,drop=FALSE]
X[,2,drop=FALSE]
colnames(X)
rownames(X)
#assign names 
rownames(X) <- c("obs1","obs2","obs3") 
X
```

* **Matrix Properties**  
```{r}
dim(X)
diag(X)
```



